---
title: "HW3"
author: "chenxi yu"
date: '2019-09-27'
output: html_document
---

# Data description

The data of this assignment is coming from https://academic.oup.com/aje/article/188/9/1733/5525028. This article analyses the impact and effectiveness of state-level tuberculosis interventions in four different locations. The data is from Table 3 in this paper. The original table shows the projected yields of targeted testing and treatment for tuberculosis in California, Florida, New York, and Texas. It provides data point estimate and 95% confidence interval of different risk type groups from the simulation study.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

**BMB**: it's good to name your code chunks (for debugging purposes)

# load data
```{r}
dd <-read.csv("Table3.csv")
# create a new dataset to store information of point estimate from the table
dd_PE <- (dd
          %>% select(risktype, info.type,PE_CL,PE_FL,PE_NY,PE_TE)
          %>% rename(California=PE_CL,Florida=PE_FL,New_York=PE_NY,Texas=PE_TE)
          %>% gather(key="location","estimates",-risktype,-info.type)
)
# create a new dataset to store information of confidence intervals
dd_CI <- (dd
          %>% select(risktype, info.type,X95..Range._CL,X95..Range._FL,X95..Range._NY,X95..Range_TE)
          %>% rename(California=X95..Range._CL,Florida=X95..Range._FL,New_York=X95..Range._NY,Texas=X95..Range_TE)
          %>% gather(key="location","CI",-risktype,-info.type)
          %>% separate(CI,c("LL","UL"),sep = "[–]")
)
# combine two subsets together
dd2 <- (left_join(dd_PE,dd_CI))
## delete "," in numerical data of upper limit and lower limit of CI
## BMB: had to be a little more drastic
dd3 <- (dd2
  %>% mutate_all(~gsub(x=.,pattern="[, _]",replacement=""))
  %>% mutate_at(c("estimates","LL","UL"),as.numeric)
)
```
#since it makes no sense to translate the x-axis into continuous scale, so errorbar drawed instead of a ribbon
```{r}
gg <- (ggplot(dd3, aes(x=risktype,y=estimates,color=location))
       + geom_point()
       + geom_errorbar(aes(ymin=LL,ymax=UL))
       + facet_grid(location~info.type)
)

print(gg)
```
# Comments on Plot
This plot shows estimation of people affected under different risk types.The dots stands for point estimates and bars for 95% confidence intervals. Different colors are used to distinguish between different groups. The main disadvantage of this plot is that the information on x-axis cannot be shown clearly. Since the label on x-axis is used to indicate risk types. So the variable is discrete on x-axis. The first two groups of data, which are no. of completing LTBI treatment and no. of active TB diagnosis is laying between a relatively shorter interval compared to no. of person screened. Especially for no. of completing LTBI, we cannot find the difference between risk types obviously.

BMB: 

* colours redundant with facets
* could have combined info.types into a single facet (e.g with line types?)
* order: why alphabetical?
* scale numbers by 1000 for easier reading?
* default colour scheme?
* confidence intervals are too small to see on this scale: log scaling? separation into facets with different scales?
* x-axis labels are unreadable: flip x/y axes?

score: 1.8

This seems much more readable (could still work on ordering, colours, etc.

```{r}
library(ggstance)
gg <- (ggplot(dd3, aes(y=risktype,x=estimates,color=location))
       + geom_pointrangeh(aes(xmin=LL,xmax=UL))
       + facet_wrap(~info.type,scale="free",ncol=1)
)
print(gg)
```
